### 2019-02-26 sections/intuition.tex
some fixmes

To model collaboration, one needs communication, concurrency, and synchronisation. \fixme{Alejandro: Is this a basic calculus to why iTasks is elaborated?} %nico: not sure what he means here...
In \TOP, collaboration is specified on a high level of abstraction, hiding the details of communication.
For example, the cigarette smokers communicate with each other, but the programs do not explicitly mention sending or receiving events.

>>>>

Collaboration in the real world consists of three aspects: communication, concurrency, and synchronisation.
These aspects are reflected in \TOP on a high level of abstraction, hiding the details of communication.
For example, the cigarette smokers communicate with each other, but the programs do not explicitly mention sending or receiving events.
